How fluid-mechanical erosion creates anisotropic porous media

### 2022-06-13 docs/PhysicsPaper/StokesErosion.tex
NM

\begin{abstract}
Using a Cauchy integral formulation of the boundary integral equations, we numerically simulation the erosion a porous medium comprised of $O(100)$ solid bodies embedded in a Stokes flow. The bodies comprising the porous medium are resolved individually and erode under the action of surface shear stress. In particular, microscopic changes in the morphology of the constituents are resolved in detail, and these changes give rise to larger-scale features such as channelization of the medium. The Cauchy-integral and barycentric quadrature formulas allows us to resolve configurations of tightly packed and nearly contacting bodies.
\end{abstract}
\maketitle

>>>>

\begin{abstract}
Using a Cauchy integral formulation of the boundary integral equations, we numerically simulation the erosion a porous medium comprised of $O(100)$ solid bodies embedded in a Stokes flow. The bodies comprising the porous medium are resolved individually and erode under the action of surface shear stress. In particular, changes in the morphology of individual bodies are resolved in detail, and these microscopic changes give rise to larger-scale features in the medium such as channelization. The Cauchy-integral and barycentric quadrature formulas allows us to resolve configurations of tightly packed and nearly contacting bodies. Armed with these methods, we observe anisotropy 
\end{abstract}
\maketitle
